\sectiondivider{Phenomenology and legacy}{How couplings, rates, and open questions line up.}

\begin{frame}{The Higgs couples in proportion to mass}
  \slidephrase{Heavier particles couple more strongly to the Higgs.}
  \slidesubphrase{Fermion couplings scale like $m_f$.}
  \slidesubphrase{Vector couplings scale like $m_V^2$.}
\end{frame}

\begin{frame}{Production}
  \slidephrase{At the LHC, Higgs bosons are produced mainly by gluon fusion.}
  \slidesubphrase{Vector boson fusion and associated production provide complementary handles.}
  \slidesubphrase{Each mode favors different experimental signatures.}
\end{frame}

\begin{frame}{Decays}
  \slidephrase{Decay patterns follow from couplings and available phase space.}
  \slidesubphrase{At $125$ GeV, many channels compete.}
  \slidesubphrase{Some are rare but exceptionally clean.}
\end{frame}

\begin{frame}{Why H $\to \gamma\gamma$?}
  \slidephrase{A loop-induced, rare decay.}
  \slidesubphrase{No tree-level coupling, but an extremely clean electromagnetic signature.}
  \slidesubphrase{Small branching ratio, high discovery power.}
\end{frame}

\begin{frame}{Why H $\to ZZ \to 4\ell$?}
  \slidephrase{Four charged leptons fully reconstruct the Higgs mass.}
  \slidesubphrase{Backgrounds are tiny and well understood.}
  \slidesubphrase{This is a golden channel.}
\end{frame}

\begin{frame}{The 125 GeV Fingerprint}
  \slidephrase{Observed rates in $\gamma\gamma$ and $ZZ\!\to\!4\ell$ match predictions.}
  \slidesubphrase{Coupling strengths follow mass–proportional patterns.}
  \slidesubphrase{Phenomenology and discovery align.}
\end{frame}

\begin{frame}{What would be wrong if this wasn't the Higgs?}
  \slidephrase{Without the Higgs, the Standard Model would fall apart.}
  \slidesubphrase{No symmetry-preserving way to give mass to $W$, $Z$, or fermions.}
  \slidesubphrase{Precision tests and unitarity would be in tension without this field.}
\end{frame}

\begin{frame}{A consistent picture emerges}
  \slidephrase{Production and decay patterns fit a $125$ GeV Higgs boson.}
  \slidesubphrase{Theory, phenomenology, and data form a unified story.}
  \slidesubphrase{This concludes the arc from mechanism to discovery.}
\end{frame}
