\sectiondivider{Symmetry breaking}{The vacuum hides the rules our equations respect.}

\begin{frame}{A symmetry… but a broken ground state}
  \slidephrase{The laws respect the symmetry.}
  \slidesubphrase{The vacuum does not.}
  \slidesubphrase{Spontaneous symmetry breaking hides the symmetry in the ground state.}
\end{frame}

\begin{frame}{A Simple Scalar Field}
  \centering
  Complex scalar field with symmetric dynamics.
  \[
    \mathcal{L} = \partial_\mu \phi^* \partial^\mu \phi - \mu^2 |\phi|^2 - \lambda |\phi|^4
  \]
\end{frame}

\begin{frame}{The Potential}
  \centering
  \[
    V(\phi) = \mu^2 |\phi|^2 + \lambda |\phi|^4
  \]
  If $\mu^2 < 0$, the minimum lies away from $\phi = 0$.
\end{frame}

\begin{frame}{Choosing a Vacuum}
  \slidephrase{The minimum lies on a circle of vacua.}
  \slidesubphrase{The vacuum picks one direction in field space.}
  \slidesubphrase{Symmetry is hidden, not destroyed.}
\end{frame}

\begin{frame}{Goldstone Modes}
  \slidephrase{Breaking a continuous symmetry creates massless excitations.}
  \slidesubphrase{Goldstone modes live along the flat directions.}
  \slidesubphrase{Goldstone's theorem in action.}
\end{frame}

\begin{frame}{Toward Massive Gauge Bosons}
  \slidephrase{Spontaneous breaking leaves the Lagrangian symmetric.}
  \slidesubphrase{Its vacuum chooses a direction.}
  \slidesubphrase{Electroweak gauge fields will use this mechanism.}
\end{frame}

\begin{frame}{Enter the Higgs Field}
  \slidephrase{Build the electroweak story with the Higgs field.}
  \slidesubphrase{Its vacuum value will complete mass generation.}
\end{frame}
